Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-09-14 fully-abstract-comp/technical-report.tex
updated the text about linear capabilities to explain why we abandon the idea of turning normal capabilities into linear capabilities.

There are multiple ways that linear capabilities could work (we choose the second one):
\begin{enumerate}
\item A linear capability comes with a system wide guarantee that no alias for this capability (or any part of the memory it has authority over). In other words, the linear capability is the only capability for this piece of memory.

@@

In this scheme, the system would initially have one non-linear capability for all of the memory. The linear capabilities would then be generated as they are needed.
\end{enumerate}
Notice that the two schemes are incompatible as they would undermine eachother.

We choose to use the second scheme for the following reasons:
\begin{enumerate}
\item While the stack pointer was the motivation for the linear capabilities, we believe they can also be used for other things such as return pointers. When used for return pointers, we know that the return pointer used to return to us was the only one available. However, if we used the first scheme, then all of the code would have to be in the linear part of memory. This would be undesirable if we want to provide several entities access to the same program. 
\end{enumerate}

>>>>

There are multiple ways that linear capabilities could work (we choose the third one):
\begin{enumerate}
\item A linear capability comes with a system wide guarantee that no alias for this capability (or any part of the memory it has authority over). In other words, the linear capability is the only capability for this piece of memory.

@@

In this scheme, the system would initially have one non-linear capability for all of the memory. The linear capabilities would then be generated as they are needed.
\item A linear capability is ``born'' with the guarantee that it is not aliased. This guarantee is maintained by the semantics. Linear capabilties cannot be converted to another kind of capability (in other words, this is option one but where linear capabilities cannot be changed).
\end{enumerate}
Notice that the two first schemes are incompatible as they would undermine eachother.

We chose to use the second scheme for the following reasons:
\begin{itemize}
\item While the stack pointer was the motivation for the linear capabilities, we believe they can also be used for other things such as return pointers. When used for return pointers, we know that the return pointer used to return to us was the only one available. However, if we used the first scheme, then all of the code would have to be in the linear part of memory. This would be undesirable if we want to provide several entities access to the same program. 
\end{itemize}
We later abandonned the second option for the following reason:
\begin{itemize}
\item The initial idea with linear capabilities was to use them for stack pointers, because there would only ever be one capability for a any part of the stack. However, when normal capabilities can become linear, then it is only the creator of the linear capability that can be sure that no alias is created from the linear capability. Someone who receives a linear capability would not be able to trust the linear capability as it might have come about as a normal capability that has been aliased and later turned linear.

In other words, we needed a system-wide guarantee to be able to put some trust in linear capabilities from untrusted a source we do not trust.
\end{itemize}
